Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
small tweak

The idea behind
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
to use $K$ copies of the \textsc{Binary Perceptron} algorithm; see e.g.
\citet[Section 3.3.1]{Shalev-Shwartz-2012}. Each copy corresponds to one of the
classes. At each time step $t$, upon seeing example $x_t$, copy $i$ makes a
binary prediction on whether $x_t$ belongs to class $i$ or not. If at least one
copy makes a positive prediction, the algorithm chooses its prediction as one of
the classes corresponding to a positive prediction. If all copies make negative
predictions, the algorithm makes a prediction uniformly at random from
$\cbr{1,\ldots,K}$.

@@

The upper bound $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$ on the expected number of
mistakes of
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
optimal up to a constant factor, as long as the number of classes $K$ is at most
$O((R/\gamma)^2)$. This lower bound is stated as
\autoref{theorem:strongly-separable-examples-mistake-lower-bound} below. The
proof of the theorem can be found in
Appendix~\ref{section:proofs-for-stringly-separable-examples} in the
supplementary material.

@@

\paragraph{Remark.}
If $\gamma \le R$ then, irrespective of any other conditions on $K$, $R$, and
$\gamma$, a trivial lower bound on the expected number of mistakes of any
randomized algorithm is $(K-1)/2$. To see this, note that the adversary can
choose an example $(R e_1, y)$, where $e_1$ is some arbitrary unit vector in $V$
and $y$ is a label chosen uniformly from $\cbr{1,2,\dots,K}$, and show this
example $K$ times. The sequence of examples trivially satisfies the strong
linear separability condition, and the $(K-1)/2$ expected mistake lower bound
follows from ~\citep[][Claim 2]{Daniely-Helbertal-2013}. However, it is unclear
if the trivial lower bound is the best possible if $K$ is large, i.e.,
$\omega((R/\gamma)^2)$. We leave this as an open problem.

>>>>

The idea behind
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
to use $K$ copies of the \textsc{Binary Perceptron} algorithm, one copy per class; see e.g.
\citet[Section 3.3.1]{Shalev-Shwartz-2012}.
Upon seeing each example $x_t$, copy $i$ predicts 
whether or not $x_t$ belongs to class $i$.
Multiclass predictions are done by evaluating all $K$ binary predictors and outputting any class with a positive prediction.  If all binary predictions are negative, the algorithm chooses a prediction a prediction uniformly at random from
$\cbr{1,\ldots,K}$.

@@

The upper bound $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$ on the expected number of
mistakes of
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
optimal up to a constant factor, as long as the number of classes $K$ is at most
$O((R/\gamma)^2)$. This lower bound is stated as
\autoref{theorem:strongly-separable-examples-mistake-lower-bound} below. The
proof of the theorem can be found in
Appendix~\ref{section:proofs-for-stringly-separable-examples} in the
supplementary material.
\citet{Daniely-Helbertal-2013} provide a lower bound under the assumption of weak linear separability, which does not immediately imply a lower bound under the stronger notion.

@@

\paragraph{Remark.}
If $\gamma \le R$ then, irrespective of any other conditions on $K$, $R$, and
$\gamma$, a trivial lower bound on the expected number of mistakes of any
randomized algorithm is $(K-1)/2$. To see this, note that the adversary can
choose an example $(R e_1, y)$, where $e_1$ is some arbitrary unit vector in $V$
and $y$ is a label chosen uniformly from $\cbr{1,2,\dots,K}$, and show this
example $K$ times. The sequence of examples trivially satisfies the strong
linear separability condition, and the $(K-1)/2$ expected mistake lower bound
follows from ~\citep[][Claim 2]{Daniely-Helbertal-2013}. %However, it is unclear
%if the trivial lower bound is the best possible if $K$ is large, i.e.,
%$\omega((R/\gamma)^2)$. We leave this as an open problem.
